MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
j
graph for win loss updated

```{r}
aa<- cast(df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + WINNER ~ W)

@@

aa2<- cast(aa, AWAY_TEAM ~ WINNER); names(aa2)[1]<-"TEAM"
aa2$WIN_PCT_AWAY<-round(aa2$HOME/(aa2$HOME+aa2$AWAY),2)

aa3<- merge (aa1,aa2, by ="TEAM")
for (i in 1:nrow(aa3)) {if(aa3$WIN_PCT_HOME[i]>aa3$WIN_PCT_AWAY[i]) aa3$HOME_ADV[i]<-"YES" else aa3$HOME_ADV[i]<-"NO"}
head(aa3)

ggplot(aa3,aes(x=TEAM, y= WIN_PCT_HOME, col= HOME_ADV))+ geom_point()
#TO BE UPDATED
```

# Shooting Percentage Analysis (James)

```{r}
# Replace "made" and "missed" with 1 and 0 respectively

df[, "SHOT_RESULT"] <- as.character(df[, "SHOT_RESULT"])

for (i in 1:nrow(df)) {
  if (df[i, "SHOT_RESULT"] == "made") df[i, "SHOT_RESULT"] <- 1
  if (df[i, "SHOT_RESULT"] == "missed") df[i, "SHOT_RESULT"] <- 0
}

df[, "SHOT_RESULT"] <- as.numeric(df[, "SHOT_RESULT"])

```{r}
# Find shooting percentage of each match

# Trying to reshape...

library(reshape)
game <- cast(data = df, GAME_ID1 ~ SHOT_RESULT)
View(game)

#

Team <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
FG_Percentage <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
for(i in 21400001:21400908){
  j = i - 21400001 +1 # 
  game <- df[, df[, "GAME_ID1"] == i]
  home <- game[, game["LOCATION"] == "H"]
  home.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / nrow(home)
  away <- game[, game["LOCATION"] == "A"]
  away.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / away(home)
  FG_Percentage[j] <- home.p
  FG_Percentage[j + 1] = away.p
  Team[j] = "H"
  Team[j + 1] = "A"
}

>>>>

```{r}
aa<- cast(df1, GAME_ID1 + HOME_TEAM + AWAY_TEAM + WINNER ~ W)

@@

aa2<- cast(aa, AWAY_TEAM ~ WINNER); names(aa2)[1]<-"TEAM"
aa2$WIN_PCT_AWAY<-round(aa2$AWAY/(aa2$HOME+aa2$AWAY),2)

aa3<- merge (aa1,aa2, by ="TEAM")

for (i in 1:nrow(aa3)) {if(aa3$WIN_PCT_HOME[i]>aa3$WIN_PCT_AWAY[i]) aa3$HOME_ADV[i]<-"YES" else aa3$HOME_ADV[i]<-"NO"}
head(aa3)

aa3<- aa3[order(aa3$WIN_PCT_HOME,decreasing=TRUE),]
rownames(aa4)<-NULL

aa3$TEAM <- factor(aa5$TEAM, levels = aa5$TEAM[order(-aa5$WIN_PCT_HOME)])

ggplot(aa3,aes(x=TEAM)) + geom_point(aes(y= WIN_PCT_HOME, col= "HOME"))+ geom_point(aes( y= WIN_PCT_AWAY, col= "AWAY")) 
#TO BE UPDATED
```
